Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-16 cav2017/cav2017.tex
cav

\todo{[Here discuss Jury criterium]}

\bigskip

\todo{[Unclear what the remainder of the section serves for. ]}
The output and measurable of the plant is being sampled by an ADC, and since the full state of the
plant cannot be witnessed directly, the controller software includes an observer that 
estimates the state of the plant (see appendix for details on how such an observer
is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  We further presume that there are small tolerances in the system 
described in the following form
%
\begin{align*}
\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
\end{align*}
\commentib{What is S?}

@@

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Verification of a Controllable Observed System}\label{sec:cof_verification}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

>>>>

\todo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantisation noises yet).]}

@@

\todo{[The remainder of the section needs to be updated. ]}
The output and measurable of the plant is being sampled by an ADC, and since the full state of the
plant cannot be witnessed directly, the controller software includes an observer that 
estimates the state of the plant (see appendix for details on how such an observer
is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
\todo{[Unclear what the remainder is for: ]}
We further presume that there are small tolerances in the system 
described in the following form
%
\begin{align*}
\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
\end{align*}
\commentib{What is S?}

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Verification of a Controllable Observed System}
\label{sec:cof_verification}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
